Compositional Equivalences Based on Open pNets

### 2022-10-18 2016-Weak-FH-Bisim/WeakBisim.tex
dernieres (?) reponses...

This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
\TODO{Eric: relations with SOS rule formats?}

@@

We define now a bisimulation relation tailored to open automata and their parametric nature. This relation relates states of the open automata and guarantees that the related states are observationally equivalent, i.e. equivalent states can trigger transitions with identical action labels. Its key characteristics are 1) the introduction of predicates in the bisimulation relation: the relation between states may depend on the value of the variables; 2)  bisimulation  relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
 We name it FH-bisimulation,
 as a short cut for the ``Formal Hypotheses'' over the holes behaviour manipulated in the
 transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
 that pioneered this idea.
\TODO{Eric: combination of RdS, symb bisim, and more}

>>>>

This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
\ERIC{This is loosely related to works on the syntactic conditions on SOS rules to check whether weak bisimulation is a congruence for some process algebra operators \cite{GrootVaandrager1992}. Our approach is semantical and more global: our sufficient condition applies to a whole (open) system, and is expressed on its open automaton (see Definition \ref{def:non-obspNet}).}
%\TODO{Eric: relations with SOS rule formats?}

@@

We define now a bisimulation relation tailored to open automata and their parametric nature. This relation relates states of the open automata and guarantees that the related states are observationally equivalent, i.e. equivalent states can trigger transitions with identical action labels. Its key characteristics are 1) the introduction of predicates in the bisimulation relation: the relation between states may depend on the value of the variables; 2)  bisimulation  relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
 We name it FH-bisimulation,
 as a short cut for the ``Formal Hypotheses'' over the holes behaviour manipulated in the
 transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
 that pioneered this idea.
\ERIC{Indeed, our definition uses both hypotheses on the behaviour of holes, as in \cite{deSimone85}, and symbolic manipulation of action expressions, as in symbolic bisimulations of \cite{HENNESSY:1995}. }
%\TODO{Eric: combination of RdS, symb bisim, and more}
